---
title: "Code for Mussel Freeze Thaw"
author: "Lauren Gill"
date: "16/12/2021"

output:
  pdf_document:
    toc: TRUE
toc-depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy=TRUE, tidy.opts = list(width.cutoff = 60))
```

## Libraries

```{r, message = FALSE}
library(MASS)
library(plyr)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(here)
library(tidyverse)
library(cowplot)
library(car)
library(multcomp)
```

## Survival

### Freeze Treatment Comparisons
Reading in Data and filtering for total freeze time to be equal to 8 hours
```{r}
survival <- read.csv(here("Data", "survival.csv"))
only.8 <- survival %>% filter(Total.freeze.time ==8)
```

Now running a chisq test on the data, using time frozen, acclimation time and position as variables
```{r}
only.8$Time_Frozen_hrs <- as.factor(only.8$Time_Frozen_hrs)
only.8.glm <- glm(Survival~Time_Frozen_hrs*Acclimation_time_days*Position,family="binomial",data=only.8)

only.8.glm.reduced <- glm(Survival~Time_Frozen_hrs,family="binomial",data=only.8)
anova(only.8.glm,test="Chisq")
summary(glht(only.8.glm.reduced, mcp(Time_Frozen_hrs="Tukey")))
```

Now seeing if length affects survival
```{r}
only.8.glm.length<- glm(Survival~Length_mm,data=only.8)
summary(aov(only.8.glm.length))
```

```{r}
only.8.group <- group_by(only.8,Time_Frozen_hrs)
only.8.sum <- summarise(only.8.group, prop_surv=mean(Survival, na.rm=TRUE), sd=sd(Survival, na.rm=TRUE), total=n(), SE=sd(Survival)/sqrt(n()))

only.8.sum$Time_Frozen_hrs <- as.factor(only.8.sum$Time_Frozen_hrs)

survivalgraph <- ggplot(only.8.sum, aes(x=Time_Frozen_hrs, y=prop_surv)) +geom_point()+ylim(0,1) +
  xlab("Freeze Treatments") + ylab("Survival Proportion") + 
  geom_errorbar(aes(ymin=prop_surv-SE, ymax=prop_surv+SE, width=.2))+
  theme_classic()+
  geom_point(size=2)+ scale_x_discrete(labels=c("2 hour x4", "4 hour x2", "8 hour x1"))

```


### Cumulative freezing

```{r}
repeat2 <-subset(survival, survival$Time_Frozen_hrs ==2)
repeat2sum <- group_by(repeat2,Culmulative_Freeze_Number)
repeat2sum1 <- summarise(repeat2sum, prop_surv=mean(Survival, na.rm=TRUE), sd=sd(Survival, na.rm=TRUE), total=n(), SE=sd(Survival)/sqrt(n()))
repeatedfreeze <- ggplot(repeat2sum1, aes(x=Culmulative_Freeze_Number, y=prop_surv)) + geom_point() +ylim(0,1) +
  xlab("Cumulative Freeze Number") + ylab("Survival Proportion")+
  geom_errorbar(aes(ymin=prop_surv-SE, ymax=prop_surv+SE, width=.2))+
  theme_classic()+
  geom_point(size=2)
```

```{r}
##combining cumulative and 8 hour total freezes
combinedsurival <- plot_grid(survivalgraph, repeatedfreeze, labels = c("A", "B"))
combinedsurival
#ggsave("survivalgraph", device = "tiff", dpi = 300, width = 174, height = 100, units = "mm")
```


## Basal Levels of HSP70

### Top Band

Reading in Data
```{r}
top_bands <-read.csv(here("Data", "Top band.csv"))
```
For Basal levels we only want to use the control mussels, because these are the mussels that were not frozen, and therefore will show us how much HSP70 they have naturally, so subset the controls and then take the mean of relative density
```{r, message = FALSE}
controlonlytop <- subset(top_bands, top_bands$treatment == 'C')
controldenstop <- controlonlytop  %>%
  group_by(position, time.frozen, sam.num)  %>%
  summarise(meanden=mean(rel.dens))
```

Now running a t.test on the control mussels to see if position makes a difference
```{r}
shapiro.test(controldenstop$meanden) #p = 0.08, its normal
bartlett.test(meanden~position, data = controldenstop) # p-value = 0.09448, Homogeneity of variances are equal
t.test(meanden~position, var.equal=FALSE, data=controldenstop)
```

Now making a box plot of basal levels
```{r}
controlboxtop <- ggplot(controldenstop, aes(x=position, y=meanden)) + 
  geom_boxplot() + ylim(0,1) +
  xlab("Position") + ylab("Relative 76 kDa Density") +
  theme_classic()+geom_jitter()
controlboxtop
```

### All bands 
Below are the same steps as with the top bands
```{r, message = FALSE}
all_bands <-read.csv(here( "Data", "All bands.csv"))
controlonlyall <- subset(all_bands, all_bands$treatment== 'C')
controldensall <- controlonlyall  %>%
  group_by(position, freeze.time, sam.num)  %>%
  summarise(meanden=mean(rel.dens))

```

```{r}
shapiro.test(controldensall$meanden) #p-value = 0.04557, not normal
##Using man whitney U test
wilcox.test(meanden~position, data=controldensall)


#Now making a box plot of basal levels - NO difference
controlbox <- ggplot(controldensall, aes(x=position, y=meanden)) + 
  geom_boxplot() + ylim(0,1) +
  xlab("Position") + ylab("Relative HSP70 Density") +
  theme_classic()+geom_jitter()
controlbox
```

### Bottom Bands
```{r, message = FALSE}
bottom_bands <-read.csv(here( "Data", "Bottom bands.csv"))

controlonlybottom <- subset(bottom_bands, bottom_bands$treatment== 'C')
controldensbot <- controlonlybottom  %>%
  group_by(shore.position, freeze.time, sample.num)  %>%
  summarise(meanden=mean(rel.dens))
```

```{r}
shapiro.test(controldensbot$meanden) #p-value = 0.09156
t.test(meanden~shore.position, var.equal=FALSE, data=controldensbot) #p-value = 0.7409

#Now making a box plot of basal levels - NO difference
controlboxbot <- ggplot(controldensbot, aes(x=shore.position, y=meanden)) + 
  geom_boxplot() + ylim(0,1) +
  xlab("Position") + ylab("Relative 68+70 kDa Density") +
  theme_classic() + geom_jitter()
controlboxbot
```

Now combining all three graphs to make one
```{r}

plot_grid(controlbox, controlboxbot,controlboxtop, ncol=3, labels= "AUTO")
ggsave("basalhsp70.tiff", device = "tiff", dpi = 300, width = 174, height = 100, units = "mm")
```

## HSP70 vs position (High intertidal/Low intertidal) and recovery time (2 or 20 hours)

### Top Bands
Make a subset of controls, and then in a seperate excel spread sheet, divide the relative densities of the top bands by the control averages. Then took the log 2 averages of those
```{r}
controlonlytop_1<- aggregate(controlonlytop$rel.dens,
                             by=list(controlonlytop$position, 
                                     controlonlytop$time.frozen, 
                                     controlonlytop$recovery), FUN=mean)
log2top <-read.csv(here("Data", "meantop.csv"))
log2top.aov <- aov(log.2.fold~position*freeze.time*recovery,data=log2top)
summary(log2top.aov)
```

### All bands

Group this data into just the experimentals, with mean densities
```{r, message = FALSE}
meandensityall <- all_bands  %>%
  group_by(treatment, position,freeze.time, recovery, sam.num)  %>%
  summarise(meanden=mean(rel.dens)) %>%
  filter(treatment == 'E')
```

Then write this into an excel sheet, copy in control values, divide by those, and then log 2 those values. Making seperate columns for each function. Read in this new data set, mutate recovery and freeze time as a factor
```{r}
#write.csv(meandensityall,here("Data", "meanall1.csv"))

log2all <- read.csv(here("Data", "meanall.csv"))
log2all$recovery <- as.factor(log2all$recovery)
log2all$freeze.time <- as.factor(log2all$freeze.time)
```

Now to run an anova on this data, first checking for normality using shapirowilk, variances using bartlett test

```{r}
shapiro.test(log2all$log.2.fold) #p-value =  0.08344, normal
bartlett.test(log.2.fold~position ,data=log2all) #p-value = 0.4231
log2all.aov <- aov(log.2.fold~position*freeze.time*recovery,data=log2all)
summary(log2all.aov)
TukeyHSD(log2all.aov)
```

### Bottom bands

```{r}
log2bottom <-read.csv(here("Data", "meanbottom1.csv"))
log2bottom$recovery <- as.factor(log2bottom$recovery)
log2bottom$freeze.time <- as.factor(log2bottom$freeze.time)
shapiro.test(log2bottom$log.2.fold) #p-value = 0.05715
bartlett.test(log.2.fold~position ,data=log2bottom) #p-value = 0.4688
log2bottom.aov <- aov(log.2.fold~position*freeze.time*recovery,data=log2bottom)
summary(log2bottom.aov)
```

### Top bands

```{r}
log2top <-read.csv(here("Data", "meantop.csv"))
log2top$recovery <- as.factor(log2top$recovery)
log2top$freeze.time <- as.factor(log2top$freeze.time)
logtop.aov <- aov(log.2.fold~position*freeze.time*recovery, data=log2top)
summary(logtop.aov)
TukeyHSD(logtop.aov)
```


### Graphing the data for freeze time vs position
All bands
```{r}
arrangedata <- ddply(log2all, c("position","freeze.time"), summarise,
                     N    = length(log.2.fold),
                     mean = mean(log.2.fold),
                     sd   = sd(log.2.fold),
                     std   = sd / sqrt(N))
pd <- position_dodge(0.01)  
#The errorbars overlapped, so use position_dodge to move them horizontally
all.bands.position <- ggplot(arrangedata, 
                             aes(x=position, y=mean, 
                                 linetype=freeze.time,group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) +
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative HSP70 Density')) +
  xlab("Position")+ theme(legend.position = "none")+
  theme_classic() +scale_color_manual(values = c("#E69F00", "#009E73"))+
  theme(text = element_text(size=9))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)),labels=c("High", "Low"))+ 
  theme(legend.position="none")+ ylim(-1.3, 1.2)
```

Bottom bands
```{r}
arrangedata.bottom <- ddply(log2bottom, c("position","freeze.time"), summarise,
                            N    = length(log.2.fold),
                            mean = mean(log.2.fold),
                            sd   = sd(log.2.fold),
                            std   = sd / sqrt(N))
pd <- position_dodge(0.01)  
bottom.bands.position <- ggplot(arrangedata.bottom, 
                                aes(x=position, y=mean, 
                                    linetype=freeze.time,group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) + 
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative 68 + 70 kDa Density')) +
  xlab("Position")+
  theme_classic()+ #+scale_color_manual(values = c("#E69F00", "#009E73"))+
  theme(text = element_text(size=9))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("High", "Low"))+ 
  theme(legend.position="none")+ylim(-1.3, 1.2)
```

Top bands
```{r}
arrangedata.top <- ddply(log2top, c("position","freeze.time"), summarise,
                         N    = length(log.2.fold),
                         mean = mean(log.2.fold),
                         sd   = sd(log.2.fold),
                         std   = sd / sqrt(N))
pd <- position_dodge(0.01)  
top.bands.position <- ggplot(arrangedata.top, 
                             aes(x=position, y=mean, 
                                 group=freeze.time, 
                                 linetype = freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.2) + 
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative 76 kDa Density')) +
  xlab("Position")+
  theme_classic() +
  theme(text = element_text(size=9))+
  scale_linetype_discrete(labels = c("4 x 2 h", "1 x 8 h"))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("High", "Low"))+
  labs(linetype='Freeze Treatment')+  ylim(-1.3, 1.2)+
  theme(legend.position="none")
```

Now plotting all together. Not shown here, but legend was added in using get.legend function in cowplot

```{r}
legend <- get_legend(top.bands.position)
fullpositiongraph<- plot_grid(all.bands.position, bottom.bands.position, 
                              top.bands.position, legend, 
                              labels = c("A", "B", "C"), 
                              label_size = 12, ncol=4, 
                              rel_widths = c(4,4,4,2.5))
fullpositiongraph

#ggsave("positionhsp70.tiff", device = "tiff", dpi = 300, width = 174, height = 90, units = "mm", bg = "white")

```
This same thing was done with the recovery data, letters to denote significance were added after in "paint".

```{r}
arrangedatar <- ddply(log2all, c("recovery","freeze.time"), summarise,
                     N    = length(log.2.fold),
                     mean = mean(log.2.fold),
                     sd   = sd(log.2.fold),
                     std   = sd / sqrt(N))
pd <- position_dodge(0.01)  #The errorbars overlapped, so use position_dodge to move them horizontally
all.bands.recovery <- ggplot(arrangedatar, aes(x=recovery, y=mean, linetype=freeze.time,group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) +
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative HSP70 Density')) +
  xlab("Recovery Time")+ theme(legend.position = "none")+
  theme_classic() +
  theme(text = element_text(size=9))+
  scale_color_manual(values = c("#E69F00", "#009E73"), labels = c("2 x 4 h", "1 x 8 h"))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("2 hours", "20 hours"))+
  theme(legend.position="none")+ ylim(-1, 1.2)
all.bands.recovery

###Bottom bands
arrangedata.bottomr <- ddply(log2bottom, c("recovery","freeze.time"), summarise,
                            N    = length(log.2.fold),
                            mean = mean(log.2.fold),
                            sd   = sd(log.2.fold),
                            std   = sd / sqrt(N))
pd <- position_dodge(0.01)  #The errorbars overlapped, so use position_dodge to move them horizontally
bottom.bands.recovery <- ggplot(arrangedata.bottomr, aes(x=recovery, y=mean, linetype=freeze.time,group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) + 
  geom_point()+
ylab(bquote(''~Log [2]~'Fold Value of Relative 68+70 kDa Density')) +
  xlab("Recovery Time")+
  theme_classic() +
  scale_color_manual(values = c("#E69F00", "#009E73"))+
  theme(text = element_text(size=9))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("2 hours", "20 hours"))+ theme(legend.position="none")+ylim(-1, 1.2)
bottom.bands.recovery

##Top
arrangedata.topr <- ddply(log2top, c("recovery","freeze.time"), summarise,
                         N    = length(log.2.fold),
                         mean = mean(log.2.fold),
                         sd   = sd(log.2.fold),
                         std   = sd / sqrt(N))
pd <- position_dodge(0.01)  #The errorbars overlapped, so use position_dodge to move them horizontally
top.bands.recovery <- ggplot(arrangedata.topr, aes(x=recovery, y=mean, linetype=freeze.time,group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) + 
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative 76 kDa Density')) +
  xlab("Recovery Time")+
  theme_classic() +
  scale_linetype_discrete(labels = c("4 x 2 h", "1 x 8 h"))+
  theme(text = element_text(size=9))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("2 hours", "20 hours"))+
  labs(linetype='Freeze Treatment')+  ylim(-1, 1.2)+theme(legend.position="none")
top.bands.recovery

legend.recovery <- get_legend(
  # create some space to the left of the legend
  top.bands.recovery + theme(legend.box.margin = margin(0, 0, 0, 12))
)

recovery<- plot_grid(all.bands.recovery, bottom.bands.recovery, top.bands.recovery, legend.recovery, label_size = 12, ncol=4, rel_widths = c(4,4,4,2.5), labels = c("A", "B", "C"))
recovery

#ggsave("recoveryhsp70.tiff", device = "tiff", dpi = 300, width = 174, height = 90, units = "mm", bg = "white")

```

### Individual Freezes
Similar methods to those used above
```{r}
second <-read.csv(here("Data", "All bands_2.csv"))

controlsecond <- subset(second, second$treatment=="C")
controlsecond1 <- aggregate(controlsecond$dens, by=list(controlsecond$freeze.time), FUN=mean)
#write_xlsx(controllall1,"C:\\Users\\laure\\OneDrive\\Year 4\\Mussel Data\\2,4,6,8 hr experiment\\controlall.xlsx")
#write.xlsx(meandensitytop,"C:\\Users\\laure\\OneDrive\\Year 4\\Mussel Data\\2,4,6,8 hr experiment\\all.xlsx")

log2second <-read.csv(here("Data", "log2all_second.csv"))
log2.aov.second <- aov(log.2.fold~as.factor(freeze.time),data=log2second)
summary(log2.aov.second)

secondboxplot <- ggplot(log2second, aes(x=as.factor(freeze.time), y=log.2.fold)) + 
  geom_boxplot(outlier.shape = NA) + ylim(-1,1) +
  xlab("Freeze Time (h)") + ylab("Relative HSP70 Density") +
  theme_classic() + geom_jitter()
secondboxplot

#ggsave("individualfreeze.tiff", device = "tiff", dpi = 300, width = 174, height = 90, units = "mm", bg = "white")
```


## Ubiquitin

Reading in data
```{r}
ubi <-read.csv(here("Data", "Ubiquitin.csv"))
```

### Seeing if ubiquitin levels are affected by shore position or recovery time
Make a subset of controls
```{r}
ubicontrol <- subset(ubi, ubi$treatment=="C")
ubicontrol1 <- aggregate(ubicontrol$rel.dens, by=list(ubicontrol$position, ubicontrol$freeze.time, ubicontrol$recovery), FUN=mean)
```

Create an excel file with controls, use these to divide against experimentals
```{r}
#write.xlsx(control1) 
```
Then within excel divide each exp value by mean value for control and reupload the excel sheet, also take the log base 2 of all the relative densities

Then use this sheet from now on... first read in data
```{r}
log2 <-read.csv(here("Data", "Ubiquitin_modified.csv"))
```

Now do an anova on the log 2 data
```{r}
shapiro.test(log2$log.2) #p-value = 0.2554
log2.aov <- aov(log.2~position*as.factor(freeze.time)*as.factor(recovery),data=log2)
summary(log2.aov)
```

Now reducing the anova down to the basics using stepAIC
```{r}
log3.aov <- MASS::stepAIC(log2.aov)
summary(log3.aov)
TukeyHSD(log3.aov)
```

### Plotting Ubiquitin vs recovery/position graphs
First ubiqutin expression vs recovery
```{r}
log2$recovery <- as.factor(log2$recovery)
log2$freeze.time <- as.factor(log2$freeze.time)
arrangedata <- ddply(log2, c("recovery","freeze.time"), summarise,
                         N    = length(log.2),
                         mean = mean(log.2),
                         sd   = sd(log.2),
                         std   = sd / sqrt(N))
pd <- position_dodge(0.01)  
#The errorbars overlapped, so use position_dodge to move them horizontally
ubiquitin_recovery <- ggplot(arrangedata, aes(x=recovery, y=mean,
                                              linetype=freeze.time,
                                              group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) + 
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative Ubiquitin Density')) +
  xlab("Recovery Time")+
  theme_classic() +
  theme(text = element_text(size=9))+
  scale_color_manual(values = c("#E69F00", "#009E73"), labels = c("4 x 2 h", "1 x 8 h"))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("2 hours", "20 hours"))+
  labs(color='Freeze Treatment')+  ylim(-0.3, 0.2)+theme(legend.position="none")
ubiquitin_recovery

```

Ubiqutin vs position
```{r}
arrangedataposition <- ddply(log2, c("position","freeze.time"), summarise,
                     N    = length(log.2),
                     mean = mean(log.2),
                     sd   = sd(log.2),
                     std   = sd / sqrt(N))
pd <- position_dodge(0.01)  
#The errorbars overlapped, so use position_dodge to move them horizontally
ubiquitin_position <- ggplot(arrangedataposition, aes(x=position, y=mean, 
                                                      linetype=freeze.time,
                                                      group=freeze.time)) + 
  geom_errorbar(aes(ymin=mean-std, ymax=mean+std), width=.1, position=pd) +
  geom_line(size=1.3) + 
  geom_point()+
  ylab(bquote(''~Log [2]~'Fold Value of Relative Ubiquitin Density')) +
  xlab("Position")+
  theme_classic() +
  theme(text = element_text(size=9))+
  scale_linetype_discrete(labels = c("4 x 2 h", "1 x 8 h"))+
  geom_hline(yintercept=c(0), linetype="dashed")+
  scale_x_discrete(expand=expansion(mult=c(0.2,0.2)), labels=c("High", "Low"))+
  labs(linetype='Freeze Treatment')+  ylim(-0.25, 0.15)+theme(legend.position="none")
ubiquitin_position
```

Combining the graphs
```{r}
legend.ubiqutin <- get_legend(
  # create some space to the left of the legend
  ubiquitin_position + theme(legend.box.margin = margin(0, 0, 0, 12))
)
ubiqutin <- plot_grid(ubiquitin_recovery, ubiquitin_position, 
                      legend.ubiqutin, ncol=3, rel_widths = c(3, 3, 2), 
                      labels = c("A", "B"))
ubiqutin

#ggsave("ubiquitinlinegraph", device = "tiff", dpi = 300, width = 174, height = 90, units = "mm", bg = "white")

```


### Basal expression of Ubiquitin
Only use controls, these are the only ones needed for basal expression, now aggregate this subset to group it by position (H vs L intertidal)
```{r}
highlow <-aggregate(ubicontrol$rel.dens, by=list(ubicontrol$position), FUN=mean)
shapiro.test(ubicontrol$rel.dens) # p-value = 5.61e-05, not normal
wilcox.test(rel.dens~position, data=ubicontrol) #p-value = 0.3556
```

Now making a box plot of basal levels
```{r}
ubi_basal <- ggplot(ubicontrol, aes(x=position, y=rel.dens)) + 
  geom_boxplot() + ylim(0,2.5) +
  xlab("Position") + ylab("Relative Ubiquitin Density") + 
  theme_classic()+geom_jitter() + scale_x_discrete(labels = c("High", "Low"))
ubi_basal
```

## Correlation between HSP and ubiqutuin

Modified the HSP and ubiquitin data to make 2 new CSVs with just the means of ubiquitin and HSP on the. One has the averages across treatment groups, the other has the value for each sample
```{r}
compdata <-read.csv(here("Data", "Correlation btw hsp and ub.csv"))
sampledata <- read.csv(here("Data", "Sample correlation btw hsp and ub.csv"))
```

First check assumptions for ub and hsp, line is linear so it works
```{r}
regcomp <- ggscatter(compdata, x="ub", y="hsp", add = "reg.line", 
          conf.int =  TRUE, cor.coef = TRUE, cor.method = "pearson", 
          xlab = "Relative Ubiquitin Value", ylab = "Relative HSP70 Value")
shapiro.test(compdata$ub)
##Data = normal, p value = 0.38 
shapiro.test(compdata$hsp)
##Data is normal, p value = 0.28

##THen check assumptions for log.2 hsp and ub##############
logcomp <- ggscatter(compdata, x="log.ub", y="log.hsp", add = "reg.line", 
          conf.int =  TRUE, cor.coef = TRUE, cor.method = "pearson", 
          xlab = "Log  Ubiquitin Value", ylab = "Log  HSP Value")
##Line is also linear so it works

shapiro.test(compdata$log.ub)
##Data = normal, p value = 0.3916 
shapiro.test(compdata$log.hsp)
##Data is normal, p value = 0.832
```

### Testing for correlation
```{r}
## un-log transformed data
hsp.ub <- cor.test(compdata$ub, compdata$hsp, 
                method = "pearson")
hsp.ub
hsp.ub$p.value  #0.006917628
hsp.ub$estimate #0.8542599  

## log transformd data
log.hsp.ub <- cor.test(compdata$log.ub, compdata$log.hsp, 
                   method = "pearson")
log.hsp.ub
log.hsp.ub$p.value  #0.0104069
log.hsp.ub$estimate #0.8320211  
```

### Plotting correlation graphs

Sample by sample graphs
```{r}
sample <- ggscatter(sampledata, x="ub", y="hsp", add = "reg.line", 
          conf.int =  TRUE, cor.coef = TRUE, cor.method = "pearson", 
          xlab = "Relative Ubiquitin Value", ylab = "Relative HSP70 Value")

fulltreatment <- ggscatter(compdata, x="ub", y="hsp", add = "reg.line", 
          conf.int =  TRUE, cor.coef = TRUE, cor.method = "pearson", 
          xlab = "Relative Ubiquitin Value", ylab = "Relative HSP70 Value")
```

Combining plots
```{r}
combinedplot <- plot_grid(sample, fulltreatment, labels = c("A", "B"))
combinedplot
```

